Can greedy-like heuristics be useful for solving the Weighted Orthogonal Art Gallery Problem under regular grid discretization?

### 2020-10-11 doc/paper.tex
update

	Treba primjetiti da iz pokrivenosti diskretizacije D(P) skupom stražara iz Z ne slijedi pokrivenost poligona P istim skupom stražara Z. Na slici 1.1\fxnote{pogresna referenca 1.1, mislis na 1...} pod a) prikazan je poligon koji nije pokrivan, dok je njegova diskretizacija pokrivena. Trokut na dnu poligona predstavlja nepokrivenu regiju. Poligon na slici 1 pod b) je pokriven kao i njegova diskretizacija. \fxnote{Milane, mislm da ti slika pod a) ne odgovara svrsi. Recimo ovaj poligon se cak moze pokriti sa jednim covrom, jesam u pravu? Treba nam poligon koji se ne moze pokriti bilo kojim odabirom cvorova (cuvara)?}

@@

        From the numerical results, we observe the following conclusions concerning exact solving:
        \begin{itemize}
        	\item  \textsc{Cplex} could solve all solution to prove optimality within a fraction of a second;
        	\item   \textsc{Cp} was able to solve all those instances with weight $W1$ but with significantly more time than the time required from \textsc{Cplex};
        	\item For the subset of instances $MinArea$ which includes weight $W0$, the performance of Cp degrades significantly, which can be seen  by the respective average runtime and the number of proven optimal solutions found (67/97).
        \end{itemize}
     From the numerical results, we observe the following conclusions concerning heuristic solving:
     \begin{itemize}
     	\item  In case of the instances that include small--area polygons ($Minarea$) and weight $W0$ (Table~(\ref{small_wo})): A novel \textsc{Greedy-2} was able to significantly outperform the \textsc{Greedy-1} from literature. In this case, the best performing heuristic algorithms is hybrid \textsc{Greedy-2+Cplex} which needs the two order of magnitude lower average runtime to finish than the pure greedy methods. The average runtimes of all four heuristic methods are an order of magnitude lower than the average runtime of \textsc{Cplex}. Pure greedy methods deliver solutions of reasonable quality within 20\% of the quality of optimal solutions but needs the time which is 7-8 times lower then the average runtime of \textsc{Cplex}. Although all heuristic methods could not achieve optimal solutions (with the exception of two cases for \textsc{Greedy-1+Cplex} heuristics), the average standard deviation w.r.t. optimal solution is rather small. From last two columns, it is evident that both hybrid variants are more successful, hitting more than a half best solution each, with very small average standard deviation. 
     	\item  In case of the instances that include small-area polygons and weight $W1$ (Table~\ref{small_w1}): the best heuristic approach is \textsc{Greedy-2+Cplex} which is able to deliver solutions which are within 3\% of the optimum ones. Note that in 81 instances (out of 91) \textsc{Greedy-2+Cplex} is able to deliver equally good or better results that the other heuristic approaches. As it was the case  of the weight $W0$, heuristic methods could not achieve many optimal solutions, but average standard deviation is rather small.
     	The results of pure greedy method \textsc{Greedy-1} outperform the results of \textsc{Greedy-2}. These two methods are effective since they deliver solutions which are within 10\% of the \textsc{Cplex} results but need 3 times less runtime. The result of \textsc{Greedy-1} match just in two cases to the optimum.

     	\item In case of the instances that include large-area polygons ($FAT$) and weight $W0$ (Table~(\ref{large_w0}): the exact \textsc{Cplex} approach is a clear winner concerning average solutions' quality as well as the average runtimes;  the best heuristic algorithm w.r.t. solution quality is \textsc{Greedy-2 +Cplex}. It also matches in the most cases (on 6 instances) to the optimum results w.r.t. other heuristic approaches. Its average results are within 22\% of the average of  optimal solutions.  The pure \textsc{Greedy-1} slightly outperforms the pure greedy \textsc{Greedy-2}. It is interesting that \textsc{Greedy-1} assigns in average a  higher number of guards in comparison to the average number of guards of \textsc{Greedy-2}. The runtimes of our heuristic approaches are an order of magnitude lower than the time of \textsc{Cplex} approach. Reason for that can be seen in the used regular discretization of the polygon. For the polygons with a larger area, more points are involved in the discrete set $D(P)$ and, therefore, iterations of greedy methods take a longer time than in case when $D(P)$ is smaller (which was the case of \emph{Minarea} polygons).
     	\item  In case of the instances that include large-area polygons ($FAT$) and weight $W1$ (Table~(\ref{large_w1}): the best heuristic algorithms w.r.t. solution quality is \textsc{Greedy-1+Cplex} which is able to match in 96 instances the quality of optimal solutions. Slightly worse results are delivered by \textsc{Greedy-1} and \textsc{Greedy-2}. The obtained (heuristic) solutions of these two approaches are within 1\% of optimal solutions and they are
     	able to reach the quality of the optimal solution for 92 instances. Unfortunately, the runtimes in comparison to the runtimes of \textsc{Cplex} are significantly higher for all of our heuristic approaches. However, the average runtime for \textsc{Cp} is a bit higher that the avg. runtimes of the heuristic approaches. Again, average standard deviation for each heuristic method is rather small, indicating the good quality of the proposed algorithms.
     	\item \fxnote{TODO: pokrivenost...}
     \end{itemize}
    \fxnote{Milan: generisati vrijeme izvrsavanja svakog od algoritama, dakle, $x$-osa predstavlja sljedece parove: (Smallarea, W0), (Smllarea, W1), (FAT, W0), (FAT, W1), i onda za svaku od ovih kategorija, prikazi box-plotove za 6 nasih algoritama koji prikazuju njihova vremena izvrsavnja na $y$ osi (predstavi ih razlicitim bojama, ubaci i liegendu u gornjem desnom uglu) -- ove brojeve nadji u Tabelama 1-4,  kolona 3 ($t[s]$). U zavisnosti od prikaza, koristiti log skaliranje za y-osu.... }

>>>>

	Treba primjetiti da iz pokrivenosti diskretizacije D(P) skupom stražara iz Z ne slijedi pokrivenost poligona P istim skupom stražara Z. Na slici 1.1\fxnote{pogresna referenca 1.1, mislis na 1...} pod a) prikazan je poligon koji nije pokrivan, dok je njegova diskretizacija pokrivena. Trokut na dnu poligona predstavlja nepokrivenu regiju. Poligon na slici 1 pod b) je pokriven kao i njegova diskretizacija. \fxnote{Milane, mislm da ti slika pod a) ne odgovara svrsi. Recimo ovaj poligon se cak moze pokriti sa jednim covrom, jesam u pravu? Ubaciti tezine, i tacke diskretizacije}

@@

        From the numerical results, we observe the following conclusions concerning exact solving:
        \begin{itemize}
        	\item  \textsc{Cplex} could solve all solution to prove optimality within a fraction of a second;
        	\item   \textsc{Cp} was able to solve all those instances with weight $W1$ but with significantly more time than the time required from \textsc{Cplex};
        	\item For the subset of instances $MinArea$ which includes weight $W0$, the performance of Cp degrades significantly, which can be seen  by the respective average runtime and the number of proven optimal solutions found (67/97).
        \end{itemize}
     From the numerical results, we observe the following conclusions concerning heuristic solving:
     \begin{itemize}
     	\item  In case of the instances that include small--area polygons ($Minarea$) and weight $W0$ (Table~(\ref{small_wo})): A novel \textsc{Greedy-2} was able to significantly outperform the \textsc{Greedy-1} from literature. In this case, the best performing heuristic algorithms is hybrid \textsc{Greedy-2+Cplex} which needs the two order of magnitude lower average runtime to finish than the pure greedy methods. The average runtimes of all four heuristic methods are an order of magnitude lower than the average runtime of \textsc{Cplex}. Pure greedy methods deliver solutions of reasonable quality within 20\% of the quality of optimal solutions but needs the time which is 7-8 times lower then the average runtime of \textsc{Cplex}. Although all heuristic methods could not achieve optimal solutions (with the exception of two cases for \textsc{Greedy-1+Cplex} heuristics), the average standard deviation w.r.t. optimal solution is rather small. From last two columns, it is evident that both hybrid variants are more successful, hitting more than a half best solution each, with very small average standard deviation. 
     	\item  In case of the instances that include small-area polygons and weight $W1$ (Table~\ref{small_w1}): the best heuristic approach is \textsc{Greedy-2+Cplex} which is able to deliver solutions which are within 3\% of the optimum ones. Note that in 81 instances (out of 91) \textsc{Greedy-2+Cplex} is able to deliver equally good or better results that the other heuristic approaches. As it was the case  of the weight $W0$, heuristic methods could not achieve many optimal solutions, but average standard deviation w.r.t. optimal solutions is rather small.
     	The results of pure greedy method \textsc{Greedy-1} outperform the results of \textsc{Greedy-2}. These two methods are effective since they deliver solutions which are within 10\% of the \textsc{Cplex} results but need 3 times less runtime. The result of \textsc{Greedy-1} match just in two cases to the optimum.

     	\item In case of the instances that include large-area polygons ($FAT$) and weight $W0$ (Table~(\ref{large_w0}): the exact \textsc{Cplex} approach is a clear winner concerning average solutions' quality as well as the average runtimes;  the best heuristic algorithm w.r.t. solution quality is \textsc{Greedy-2 +Cplex}. It also matches in the most cases (on 6 instances) to the optimum results w.r.t. other heuristic approaches. Its average results are within 22\% of the average of  optimal solutions.  The pure \textsc{Greedy-1} slightly outperforms the pure greedy \textsc{Greedy-2}. It is interesting that \textsc{Greedy-1} assigns in average a  higher number of guards in comparison to the average number of guards of \textsc{Greedy-2}. The runtimes of our heuristic approaches are an order of magnitude lower than the time of \textsc{Cplex} approach. Reason for that can be seen in the used regular discretization of the polygon. For the polygons with a larger area, more points are involved in the discrete set $D(P)$ and, therefore, iterations of greedy methods take a longer time than in case when $D(P)$ is smaller (which was the case of \emph{Minarea} polygons).
     	\item  In case of the instances that include large-area polygons ($FAT$) and weight $W1$ (Table~(\ref{large_w1}): the best heuristic algorithms w.r.t. solution quality is \textsc{Greedy-1+Cplex} which is able to match in 96 instances the quality of optimal solutions. Slightly worse results are delivered by \textsc{Greedy-1} and \textsc{Greedy-2}. The obtained (heuristic) solutions of these two approaches are within 1\% of optimal solutions and they are
     	able to reach the quality of the optimal solution for 92 instances. Unfortunately, the runtimes in comparison to the runtimes of \textsc{Cplex} are significantly higher for all of our heuristic approaches. However, the average runtime for \textsc{Cp} is a bit higher that the avg. runtimes of the heuristic approaches. Again, average standard deviation for each heuristic method is rather small w.r.t. optimal solutions, indicating the good quality of the proposed algorithms.
     	\item \fxnote{TODO: pokrivenost...}
     \end{itemize}
    \fxnote{Milan: generisati vrijeme izvrsavanja svakog od algoritama, dakle, $x$-osa predstavlja sljedece parove: (Smallarea, W0), (Smllarea, W1), (FAT, W0), (FAT, W1), i onda za svaku od ovih kategorija, prikazi box-plotove za 6 nasih algoritama koji prikazuju njihova vremena izvrsavnja na $y$ osi (predstavi ih razlicitim bojama, ubaci i liegendu u gornjem desnom uglu) -- ove brojeve nadji u Tabelama 1-4,  kolona 3 ($t[s]$). U zavisnosti od prikaza, koristiti log skaliranje za y-osu.... }
